CudeleFS: Programmable Consistency and Durability\\in a Global Namespace

### 2017-04-01 paper/sections/5_implementation.tex
Uses times as main font (#16)

>>>>

\begin{listing}
\begin{minted}[frame=single,
               framesep=3mm,
               xleftmargin=21pt,fontsize=\footnotesize,
               tabsize=4]{js}
{     
    "allocated_inodes": "100000"
    "interfere_policy": "block"
    "consistency": "create"
    "durability": "local_persist"
}
\end{minted}
\caption{Implementing DeltaFS with CudeleFS.}
\label{src:deltafs}
\end{listing}

\begin{listing}
\begin{minted}[frame=single,
               framesep=3mm,
               xleftmargin=21pt,fontsize=\footnotesize,
               tabsize=4]{js}
{     
    "allocated_inodes": "100000"
    "interfere_policy": "block"
    "consistency": "create+volatile_apply"
    "durability": "local_persist"
}
\end{minted}
\caption{Implementing BatchFS with CudeleFS.}
\label{src:batchfs}
\end{listing}
